\vspace{-15mm}\fontsize{21pt}{10pt}\selectfont\textbf{Wordy Manuscript Title: \\Even Wordier Manuscript Subtitle\thanks{Draft manuscript. Please do not cite without the authors' permission.}}

### 2022-09-30 sections/results.tex
Update on Overleaf.

  The analysis of the rewiring of associations in the ASD samples with respect to the control provides a guide for the identification of key genera that could be linked to dysbiosis.
  We observed 22 unique links in the network for control samples, 12 unique links in the network for ASD subjects, and 7 edges in common between the two networks.
  Although these unique associations do not imply actual interactions, they can still serve as potential starting points for literature surveys and further experimental exploration of mechanistic processes underlying dysbiosis.
  For example, \textit{Prevotella} and \textit{Porphyromonas}, genera previously implicated in ASD~\cite{Kang2017,hoGutMicrobiotaChanges2020} and cognitive impairment~\cite{chiPorphyromonasGingivalisInducedCognitive2021} display modified connectivity in our network, suggesting that the observed associations may be relevant for understanding the role of these bacteria in disease.
  Additional visualization and comparison of networks can be performed using the \acl{mind}~\cite{huResourceComparisonIntegration2022}.

  Figure~\ref{fig:figure_s7} shows a sensitivity analysis in which we compared the default network against networks generated by altering one of the steps of the pipeline relative to the default.
  This result, both visually (Figure~\ref{fig:figure_s7}A), and quantitatively (Figure~\ref{fig:figure_s7}B)  suggests that the most significant changes occur when the \ac{op} or \ac{ta} steps are changed from the default value.

>>>>

  The analysis of the rewiring of associations in the ASD samples with respect to the control provides a guide for the identification of key genera that could be linked to dysbiosis.
  We observed 22 unique links in the network for control samples, 12 unique links in the network for ASD subjects, and 7 edges in common between the two networks.
  Although these unique associations do not imply actual interactions, they can still serve as potential starting points for literature surveys and further experimental exploration of mechanistic processes underlying dysbiosis.
  For example, \textit{Prevotella} and \textit{Porphyromonas}, genera previously implicated in ASD~\cite{Kang2017,hoGutMicrobiotaChanges2020} and cognitive impairment~\cite{chiPorphyromonasGingivalisInducedCognitive2021} display modified connectivity in our network, suggesting that the observed associations may be relevant for understanding the role of these bacteria in disease.
  Additional visualization and comparison of networks can be performed using the \acf{mind}~\cite{huResourceComparisonIntegration2022}.

  Figure~\ref{fig:figure_s7} shows a sensitivity analysis in which we compared the default network against networks generated by altering one of the steps of the pipeline relative to the default.
  This result, both visually (Figure~\ref{fig:figure_s7} A), and quantitatively (Figure~\ref{fig:figure_s7} B)  suggests that the most significant changes occur when the \ac{op} or \ac{ta} steps are changed from the default value.
